Overview and Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE1)

### 2014-03-31 WSSSPE1_report/WSSSPE1_summary_report.tex
Heiland et al summary for Implementing Policy.

Krintz et al~\cite{Krintz_WSSSPE} describe how in an era in which computing frequently takes place in a distributed cloud, the control over digital resources is increasingly shifting from physical infrastructure to APIs, in particular web-service APIs. Yet, as Krintz et al observe, although science communities have (for the most part) developed solid practices for managing physical IT infrastructure in data centers, corresponding practices and technology for API governance, refered to by Krintz et al as the ``combined policy, implementation, and deployment control'', is far less developed. As Krintz et al demonstrate, web APIs can and do change, sometimes quite frequently. raising the need to port dependent applications. The effort required for porting is notoriously difficult to estimate, making it nearly impossible for IT organizations to assess and thus properly manage the impact of API changes. To address this, Krintz et al propose a mechanism that evaluates the porting effort between two versions of a web-service API in a formal and automated way. To analyze the porting effort, they divide API changes into \emph{syntactic similarity}, the changes in inputs and outputs, and into \emph{semantic similarity}, the changes in the API's behavior. In initial tests, their method showed good congruence with human developers in scoring porting effort, offering the possibility that API governance can become as solid a part of scientific IT management as data center infrastructure management is today.

% Next, we’ll look at issues of software security.

% Heiland et al from the Center for Trustworthy Scientific Infrastructure discussed issues related to implementing strong security measures for scientific software. 
% They point out that cybersecurity is rarely addressed in scientific software design.

% Security considerations for software vary depending on the maturity level of the software package.
% But when we initially develop scientific software, we generally don’t know what the final maturity level will be.
% Scientific software developers are probably not aware of best practices for cybersecurity.
% So the authors introduce the concept of Software Security Maturity Models, such as OpenSAMM and BSI-MM. 
% These are used in industry to identify and define security vulnerabilities at different stages of the software life cycle.

% They suggest that a similar Software Security Maturity Model can formalize this process:
% It provides classification of software security practices.
% It provides a path for tightening security practices as a package’s maturity level increases.
% It emphasizes understandability over complexity.

>>>>

Krintz et al~\cite{Krintz_WSSSPE} describe how in an era in which
computing frequently takes place in a distributed cloud, the control
over digital resources is increasingly shifting from physical
infrastructure to APIs, in particular web-service APIs. Yet, as Krintz
et al observe, unlike for physical IT infrastructure in data centers,
science communities have developed very little in the way of practices and
technology for API governance, refered to by Krintz et al as the
``combined policy, implementation, and deployment control''. Web APIs
can and do change, sometimes quite frequently. raising the need to
port dependent applications. The effort required for porting is
notoriously difficult to estimate, making it nearly impossible for IT
organizations to assess and thus properly manage the impact of API
changes. To address this, Krintz et al propose a mechanism that
evaluates the porting effort between two versions of a web-service API
in a formal and automated way. To analyze the porting effort, they
divide API changes into \emph{syntactic similarity}, the changes in
inputs and outputs, and into \emph{semantic similarity}, the changes
in the API's behavior. In initial tests, their method showed good
congruence with human developers in scoring porting effort, offering
the possibility that API governance can become as solid a part of
scientific IT management as data center infrastructure management is
today.

Another aspect of sustainable software that is rarely given due
diligence in scientific software design is software security. Heiland
et al~\cite{Heiland_WSSSPE} discuss how the security measures
appropriate for scientific software strongly depend on the maturity
level of the software. However, the maturity level of a software
project meant to be sustained changes tremendously over its
development life cycle, and the eventual maturity level is often
difficult to predict during initial development. Best practice models
for identifying and defining cybersecurity vulnerabilities at
different stages of the software life cycle have been formalized as
Software Security Maturity Models. Although these are widely used in
industry, awareness among scientific software development communities
is low. Developing such models for scientific software would align
well with the objective of providing implementation approaches that
the scientific community can actually follow: A Software Security
Maturity Model provides a path to tightening security practices as
software matures, emphasizes understandability over complexity, and
classifies cybersecurity-pertinent practices for easy recognition of
what level of cybersecurity a software addresses.
